---
title: "Weight of Fish"
author: "Kimberly Lemus Munoz"
date: "summer 2022"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```






```{r}
All_Fish <-read.csv(file="Fish.csv")
```



# Predicting Fish Weight





## Perch


```{r}
Perch <- filter(All_Fish, Species =="Perch")
```


```{r}
Perch <-select(Perch, -Species)
```


### Best Models


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best model for Perch are width and height.The reason why it is the highest up on the y-axis.


### Best Two regressor model


The best two regressor model is height and width.The graph tells us it is the best 2 
regressor model because it is the model places on the graph.Landing on subset size on 2 and on Y linear 0.9400.


## Pike
```{r}
Pike <- filter(All_Fish, Species=="Pike")
```


```{r}
Pike <-select(Pike,-Species)
```





### Best Models



```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


The best model is lenght1,lenght2,lenght3 height anad width.The for is is because has the highest adjusted r value, it is the one highest on the y-axis.




### Best Two regressor model

The best two regressor model is the length1 and length3.The reason for is the graph tells us that it was the best in the 2 gregressor model,shown on the x-axis.


## Roach

```{r}
Roach <- filter(All_Fish, Species== "Roach")
```

```{r}
Roach <-select(Roach, -Species)
```


### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```




### Best Models

The best model is length 3 and the width because it has the highest adjusted r squared.It is the furthest upward on the y-axis. looking at the date L3 and lenght is on the topof all the other models with being at almost 0.850.

### Best Two regressor model

The best two regressor models are length 3 and width the reason for it gave us a the highest adjusted r squared and the squared and the graph placed it as the best model regressor 2 model and adjusted R square is on 0.850. 



## Final Summary Statements

In conclusion we were able to see the two best regressor models for the three types of fishes listed, we can see some similarities and as well some differences. Like for the perch they have the same best regressor as the pike. They both have height and width as their best regressors.As for the differences the roach has length 3 and the perch doesn't have that.